Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion

### 2023-07-31 Manuscript.Rmd
frontpage

---
title: "Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion"
author: 
  - name : "Alexandra G. Mitchell"
    affiliation : "1"
  - name : "Jesper Fischer Ehmsen"
    affiliation : "1"
  - name : "Daniel Elmstrom Christensen"
    affiliation : "2"
  - name : "Anna Villaume Stuckert"
    affiliation : "3"
  - name : "Patrick Haggard"
    affiliation : "4"  
  - name : "Francesca Fardo"
    affiliation : "1"  
affiliation:
  - id : "1"
    institution : "Center of Functionally Integrative Neuroscience (CFIN), Department of Clinical Medicine, Aarhus University, Denmark"
  - id : "2"
    institution : "Interacting Minds Center (IMC), Department XXX, Aarhus University, Denmark"
  - id : "3"
    institution : "Departement of Neuroscience, University of Copenhagen, Denmark"
  - id : "4"
    institution : "Institute of Cognitive Neuroscience, University College London, United Kingdom"
  - id : "5"
    institution : "Danish Pain Research Center, Aarhus University, Denmark"
#date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
  html_document: default
  word_document:
bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
link-citations: yes
linkcolor: blue
always_allow_html: yes
editor_options: 
  markdown: 
    wrap: sentence
---

@@

# Supplementary material
```{r,warning = F, message = F, echo = F}

get_main_tables(model_cold_exp1,round = 2, title = "Cold reference on cold ratings") %>% 
  width(j=1, width = 2.5) %>% 
  width(j=c(2,3,4,5), width = 1.1)

get_main_tables(model_warm_exp1,round = 2, title = "Cold reference on warm ratings") %>% 
  width(j=1, width = 2.5) %>% 
  width(j=c(2,3,4,5), width = 1.1)

get_main_tables(model_burn_exp1,round = 2, title = "Cold reference on burning ratings") %>% 
  width(j=1, width = 2.5) %>% 
  width(j=c(2,3,4,5), width = 1.1)

get_main_tables(model_cold_exp2,round = 2, title = "Warm reference on cold ratings") %>% 
  width(j=1, width = 2.5) %>% 
  width(j=c(2,3,4,5), width = 1.1)

get_main_tables(model_warm_exp2,round = 2, title = "Warm reference on warm ratings") %>% 
  width(j=1, width = 2.5) %>% 
  width(j=c(2,3,4,5), width = 1.1)

get_main_tables(model_burn_exp2,round = 2, title = "Warm reference on burning ratings") %>% 
  width(j=1, width = 2.5) %>% 
  width(j=c(2,3,4,5), width = 1.1)

>>>>

---
title: "Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion"
author: Alexandra G. Mitchell^1^,
        Jesper Fischer Ehmsen^1^,
        Daniel Elmstrom Christensen^1^,
        Anna Villaume Stuckert^2^,
        Patrick Haggard^3^,
        Francesca Fardo^1,4^
output:
  word_document:
      reference_docx: knitting files/test_markdown.docx
  html_document:
    css: knitting files/style.css
  pdf_document:
    latex_engine: xelatex
bibliography: knitting files/Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion.bib
link-citations: yes
linkcolor: blue
serif: Times New Roman
always_allow_html: yes
editor_options: 
  markdown: 
    wrap: sentence
---

::: {custom-style="Title text"}
^1^Center of Functionally Integrative Neuroscience, Department of Clinical Medicine, Aarhus University, Denmark

^2^Department of Neuroscience, Copenhagen University, Denmark

^3^Institute of Cognitive Neuroscience, University College London, United Kingdom

^4^Danish Pain Research Center, Department of Clinical Medicine, Aarhus University, Denmark
:::

<br>

Corresponding authors: Alexandra G. Mitchell (agmitchell@cfin.au.dk) and Francesca Fardo (francesca@cfin.au.dk)

@@

# Supplementary material
```{r,warning = F, message = F, echo = F}
get_main_tables(model_cold_exp1,round = 2, title = "Cold reference on cold ratings") %>%
  width(j=1, width = 2.5) %>%
  width(j=c(2,3,4,5), width = 1.1)%>%
  fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")

get_main_tables(model_warm_exp1,round = 2, title = "Cold reference on warm ratings") %>%
  width(j=1, width = 2.5) %>%
  width(j=c(2,3,4,5), width = 1.1)%>%
  fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")

get_main_tables(model_burn_exp1,round = 2, title = "Cold reference on burning ratings") %>%
  width(j=1, width = 2.5) %>%
  width(j=c(2,3,4,5), width = 1.1)%>%
  fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")

get_main_tables(model_cold_exp2,round = 2, title = "Warm reference on cold ratings") %>%
  width(j=1, width = 2.5) %>%
  width(j=c(2,3,4,5), width = 1.1)%>%
  fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")

get_main_tables(model_warm_exp2,round = 2, title = "Warm reference on warm ratings") %>%
  width(j=1, width = 2.5) %>%
  width(j=c(2,3,4,5), width = 1.1)%>%
  fontsize(size = 10, part = "all")%>% flextable::font(fontname = "Times New Roman", part = "all")

get_main_tables(model_burn_exp2,round = 2, title = "Warm reference on burning ratings") %>%
  width(j=1, width = 2.5) %>%
  width(j=c(2,3,4,5), width = 1.1)%>%
  fontsize(size = 10, part = "all") %>% flextable::font(fontname = "Times New Roman", part = "all")
